### 2025-07-05 Text/Thesis/Chapters/Chapter1.qmd
thesis update

Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021; @Zeng2020]. SAR imagery finds extensive applications in environmental monitoring, disaster management, agriculture mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023]. Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013;@Choi2019].

@@

To propose and evaluate entropy-based statistical tests for detecting heterogeneity in SAR imagery, using non-parametric estimation and bootstrap correction to enhance accuracy in small-sample scenarios.

>>>>

Synthetic Aperture Radar (SAR) technology has become essential in  remote sensing, as it offers high-resolution imaging capabilities independently of sunlight and weather conditions, thus facilitating continuous and reliable Earth observation&nbsp;[@Mondini2021; @Zeng2020]. SAR imagery finds extensive applications in environmental monitoring, disaster management, agricultural mapping, climatology, urban planning, and maritime surveillance, among others&nbsp;[@Akbarizadeh2012;@Moreira2013; @Mu2019;@Yu2023]. Despite these advantages, effective exploitation of SAR data requires a robust understanding of its unique statistical characteristics, particularly the presence of speckle noise, a granular interference pattern inherent to coherent imaging systems like SAR&nbsp;[@Argenti2013;@Choi2019].

@@

To propose and evaluate entropy-based statistical tests for detecting heterogeneity in SAR imagery, using non-parametric estimation and bootstrap bias-correction to enhance accuracy in small-sample scenarios.
